---
output:
  html_document:
    pandoc_args: [
      "+RTS", "-K64m",
      "-RTS"
    ]
---


## Steps

1. Set working directory and the file path to refer to the appropriate data set.

2. Set column names from the data set to a continuous varaible measure or discrete variable dimension.

3. After running the R code that creates the code for a SQLDeveloper table (shown below), create a TexasWeather1 and TexasWeather2 table in SQL Developer and import the data from the csv data set.

```{r}
source("../01 Data/R_ETL_1.R", echo = TRUE)
```

```{r}
source("../01 Data/R_ETL_2.R", echo = TRUE)
```


##Key for Plots
STATION - Station ID  
STATION_NAME - Name of Station  
ELEVATION - Elevation of station from sea level  
DATE_ - Date and Timestamp of collected data  
HLY_HIDX_NORMAL - Heat Index Average  
HLY_WIND_AVGSPD - Average Windspeed  
HLY_TEMP_NORMAL - Average Temperature  
HLY_WCHL_NORMAL - Avverage Wind Chill  

There are three plots for each data sets.  The first three are for TexasWeather1, the next three are for TexasWeather2, and the following three are for the combined data sets. 

The plots are followed by the Summaries and Head of each.

```{r}
source("../02 Data Wrangling/Wrangling and Visualizations.R", echo = TRUE)
```
